%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                              

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.81]{geometry}

% personal data
\name{Daniel Iván Parra Verde}{}
\email{danivpv@outlook.com}
\phone[mobile]{+52 844 7836082}               
\address{Saltillo, Coah. México}

\begin{document}

\recipient{Recipient:}{Microsoft Hiring Team}
\date{\today}
\opening{\textbf{Cover Letter}, \vspace{-1em}}

\makelettertitle

Dear Hiring Manager,

I am writing to express my interest in the Applied Scientist 
position within the Content Intelligence team for Business Chat 
at Microsoft. With a robust background in AI/ML and cloud technologies, 
I am eager to contribute to Microsoft's mission of advancing 
intelligent business solutions.

In my current role as Founder and AI Engineer at MXAI, I have 
successfully developed and deployed AI-powered solutions integrating a 
variety of services mainly from AWS, and I'm 
confident that I can very quickly translate my skills to Azure services. 
Besides, the experience obtained in previous roles with LLMs, RAG, RNNs, 
in feature-training-inference pipelines and batch ML systems directly 
relate with the responsibilities listed in the job description like 
conducting experiments, design guardrail metrics, and optimize performance 
collaborating with partners to deploy solutions to production.


During my master's studies, I crafted a custom training algorithm using 
the extended Kalman filter theory to propose numerically stable weight 
update rule for within-host viral infection forecasting which deepened 
my understanding of neural network training nuances and enhanced the 
applicability of the training algorithm to real-world problems containing noise. 
Since then, 
I have grown with projects and tooling like CometML and ZenML for experiment 
tracking, model versioning, and deployment. 
Nevertheless the passion for ML and LLMs inner working, has continued to 
lead me to 
develop cutting edge understanding of modern ML techniques such as 
Transformers, Physics Informed 
Neural Networks and LLMs pretraining, postraining, and inference, 
as showcased on my GitHub and Hugging Face 
profiles. I am deeply grateful to the authors of seminal works—such 
as Ian Goodfellow's 'Deep Learning', Maxime Labonne and colleagues' 
'LLM Engineer's Guidelines', and the collective insights behind 
'The Llama 3 Herd of Models'—whose contributions have profoundly 
enriched my understanding of deep learning and shaped my approach 
to MLOps/LLOps and large language model development. 

In work environments I am particularly proud of my innovative 
solutions at Kuona, 
where I proposed using QLora for model fine-tuning, Locally 
Interpretable Models and custom loss functions to target 
business KPIs. At Entropía AI, I spearheaded the development of 
RAG pipelines, significantly improving accuracy in QA benchmarks 
for legal and academic custom datasets critical for the 
development of Icaro AI.

As a bilingual professional with a C1 level in English, 
I have effectively led customer sales meetings and demo 
presentations. I am enthusiastic about collaborating 
closely with partners to deploy solutions to production 
and maintain quality over time through guardrail metrics 
and sanity test cases.

I am excited about the opportunity to join Microsoft and 
contribute to its success by leveraging my expertise in AI/ML 
and cloud technologies. Thank you for considering my application. 
I look forward to the possibility of discussing how I can 
contribute to your team.

Sincerely,
\makeletterclosing

\end{document}