%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Modified by Daniel Iván Parra Verde (2024)
% Modifications:
% - Used template for personal resume
% - English language version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{tex/deedy-resume-openfont}
\usepackage{multicol}
\usepackage{comment}
\usepackage{hyperref}
\usepackage{fontspec}

\begin{document}
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Daniel Iván}{Parra Verde}{ 
Tel. +52 8447836082 | \href{mailto:danivpv@outlook.com}{Mail: danivpv@outlook.com} | Address: P.C. 25297, Saltillo, Coahuila, México\\
\href{https://github.com/danivpv}{Github: danivpv}  | \href{https://danivpv.com/}{Portfolio: danivpv.com} | \href{https://www.linkedin.com/in/danivpv/}{LinkedIn: danivpv} | \href{https://huggingface.co/danivpv}{Hugging Face: danivpv} 
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{\href{http://www.fata.unam.mx/}{UNAM-CFATA}}
\descript{2021 | \href{https://www.enesjuriquilla.unam.mx/?page_id=4107}{BSc. Technology}}
\sectionsep
\subsection{\href{https://www.rug.nl/research/bernoulli/}{Groningen University (G)}}
\descript{2019 | \href{https://www.rug.nl/bachelors/artificial-intelligence/}{BSc. AI}}
\location{Netherlands; Full Scholarship}
\sectionsep

\subsection{\href{https://www.iimas.unam.mx/}{UNAM-IIMAS}}
\descript{2022 | \href{https://www.posgrado.unam.mx/matematicas/es/inicio}{MSc. Mathematics}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}


\location{Programming Languages:}
Python \textbullet{} 
TypeScript \textbullet{} 
SQL \textbullet{} 
Julia \textbullet{} 
Wolfram \textbullet{} 
Bash \\[4pt]

\location{Frameworks:}
Django \textbullet{} 
FastAPI \textbullet{} 
Airflow \textbullet{} 
React \textbullet{} 
Next.js \textbullet{} 
Prefect \\[4pt]


\location{Libraries:}
Langchain \textbullet{} 
LlamaIndex \textbullet{} 
OpenCV \textbullet{} 
Pandas \textbullet{} 
PyTorch \textbullet{} 
Scikit Learn \textbullet{} 
Numpy \textbullet{} 
SQLAlchemy \textbullet{} 
Docling \textbullet{} 
Pytest \\[4pt]

\location{Cloud Services:}
Hugging Face \textbullet{} 
AWS SageMaker \textbullet{} 
AWS S3 \textbullet{} 
AWS Lambda \textbullet{} 
AWS API Gateway \textbullet{} 
CometML \textbullet{} 
ZenML \textbullet{} 
Railway \textbullet{} 
Vercel \textbullet{} 
Stripe \textbullet{} 
Sendgrid \\[4pt]

\location{Databases:}
PostgreSQL \textbullet{} 
MongoDB \textbullet{} 
Qdrant \textbullet{} 
Redis \textbullet{} 
SQLite \\[4pt]

\location{Software Tools:}
Docker \textbullet{} 
Git \textbullet{} 
VSCode \textbullet{} 
Cursor \textbullet{} 
\LaTeX{} \textbullet{} 
Microsoft Office \textbullet{} 
Slack \textbullet{} 
Notion \\[6pt]

\location{Languages}
English ($+$C1) \textbullet{} German ($+$B1) \textbullet{} Spanish

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\location{Bachelor}
Deep Learning in \custombold{Python}(G)\\
Relational Databases in \custombold{SQL} (G)
Artificial Intelligence in \custombold{Python} (G)\\
Algorithms and Data Structures in \custombold{C} (G)\\
Linear Algebra\\
Differential Equations Series\\

\sectionsep

\location{Master}
Statistical Inference\\
Theoretic Machine Learning\\
Information Theory\\
Statistical Foundations of Privacy\\
Numerical Analysis \custombold{Python, Julia}\\
Real and Functional Analysis\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Founder \& AI Engineer}\\
\location{\href{https://mxai.dev}{MXAI} | January 2024 – Present | Remote}
\vspace{\topsep}
\begin{tightemize}
    \item Developed and deployed AI-powered solutions using \custombold{AWS Lambda}, \custombold{Redis}, and event-driven architectures, similar to \custombold{Azure Functions}, for chatbot backends with \custombold{Langchain} and \custombold{RAG}.
    \item Built corporate website using modern tech stack (\custombold{Next.js}, \custombold{TypeScript}, \custombold{Tailwind}, \custombold{shadcn/ui}) with responsive design.
    %\item Currently developing a SaaS platform for sales forecasting and revenue optimization using \custombold{AWS} and \custombold{ML} technologies.
    \item Led customer sales meetings and demo presentations, enhancing client engagement and satisfaction.
\end{tightemize}
\sectionsep

\runsubsection{Data Scientist}\\
\location{\href{https://kuona.ai/es/}{Kuona} | December 2023 – May 2024 | Remote}
\begin{tightemize}
    \item Developed \custombold{RNNs} with \custombold{PyTorch} and served them through a batch ML system using \custombold{Django} ORMs and \custombold{PostgreSQL} for client and operations team to simulate revenue management scenarios.
    \item Proposed using \custombold{QLora} for model fine-tuning and custom loss functions to improve business KPIs.
    \item Modeled competitors' pricing data and implemented LIME for demand elasticity analysis using \custombold{Pandas}, \custombold{Pytorch}, \custombold{Scikit-Learn}, and \custombold{PostgreSQL}.
\end{tightemize}
\sectionsep

\runsubsection{Data Scientist Jr.}\\
\location{\href{https://www.linkedin.com/company/entropia-ai/}{Entropía AI} | February 2023 – November 2023 | Remote}
\begin{tightemize}
    \item Led the development of \custombold{RAG} pipelines, enhancing accuracy in QA benchmarks for legal and academic datasets with \custombold{LlamaIndex}, \custombold{MongoDB}, and \custombold{LangChain}.
    \item Created \custombold{ELT} pipeline with \custombold{Python}, \custombold{bs4} and \custombold{Airflow} from scrapped Mexican Political System data into \custombold{MongoDB}.
    \item Contributed to the \custombold{agile} development of \href{http://www.icaro.ai/home/}{Icaro AI} web app hosted in \custombold{Heroku}.
\end{tightemize}
\sectionsep

\runsubsection{Developer Internship}\\
\location{\href{https://www.wolfram.com/company/}{Wolfram Research} | February 2021 – February 2022 | Remote}
\begin{tightemize}
    \item Built the \href{https://education.wolfram.com/summer-camp/}{'Wolfram Summer Camp'} app with \href{https://www.wolfram.com/wolfram-one/}{\custombold{Wolfram One's}} cloud.
    \item Rotated into \href{https://www.wolframalpha.com/}{Wolfram Alpha} software development team. 
\end{tightemize}
\sectionsep


\section{Projects}

\runsubsection{ArXiv Domain Expert LLM}\\
\location{\href{https://github.com/danivpv/LLM-ArXiv-Domain-Expert}{GitHub Repository}}
\begin{tightemize}
    \item Developed ML pipeline and created custom finetunning datasets in \custombold{Hugging Face} for ArXiv-specialized LLM, trained and deployed on \custombold{AWS SageMaker}.
    \item Utilizes \custombold{MongoDB}, \custombold{Qdrant}, \custombold{ZenML}, \custombold{CometML},  and \custombold{AWS} for infrastructure.
\end{tightemize}
\sectionsep

\runsubsection{Master Thesis: Neural Model Identification with EKF}\\
\location{\href{https://www.linkedin.com/in/esteban-a-hernandez-vargas-04724321/}{PhD. Esteban A. Hernandez-Vargas} | \href{https://www.systemsmedicine.de/Research/}{Systems Medicine of Infectious Diseases}}
\begin{tightemize}
    \item Implemented a custom training algorithm (weight update rule) for recurrent neural networks using the Extended Kalman Filter Theory.
    \item Error analysis of optimization, approximation, and statistical generalization.
\end{tightemize}
\sectionsep

\runsubsection{"Convocatoria Jóvenes Talentos 2018" CONCyTEC}\\
\location{\href{mailto:rchavez@comunidad.unam.mx}{PhD. Rafael Chávez Moreno} | \href{https://www.ingenieria.unam.mx/uat/directorio.php}{Unit of High Technology Juriquilla, Qro.}}
\begin{tightemize}
    \item Secured funding ($\$89,000$ MXN) for the design and manufacture of a Rover.
    \item Led the development of computer vision and path planning subsystems using \custombold{Python}, \custombold{Raspberry Pi}, and \custombold{Kinect} sensors.
\end{tightemize}


\end{minipage} 
\end{document}  